Meta-analysis on sex in MSSM-Penn-Pitt and HBCC ACC/DLPFC

### 2020-09-01 individual-cohorts/meta_analysis/meta-analysis_diagnosis.Rmd
Freeze analysis

```{r knit2synapse, eval=FALSE, echo=FALSE}
# rmarkdown::render("meta-analysis_diagnosis.Rmd")

library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "individual-cohorts/meta_analysis/meta-analysis_diagnosis.Rmd",
                                          parentId ="syn22315403",
                                          folderName = 'Meta-analysis on diagnosis',
                                          overwrite=TRUE)
```

>>>>

```{r knit2synapse, eval=FALSE, echo=FALSE}
# rmarkdown::render("individual-cohorts/meta_analysis/meta-analysis_diagnosis.Rmd")

library(synapser)
library(knit2synapse)
synLogin()
# knit2synapse::

createAndKnitToFolderEntity <- function(file, parentId, folderName,
                                        wikiName=NULL, overwrite=FALSE, knitmd=TRUE, ...) {

  entity <- synapser::Folder(parentId=parentId, name=folderName)
  entity <- synapser::synStore(entity, ...)

  knitfile2synapse(file=file, owner=entity, wikiName=wikiName, 
                   overwrite=overwrite, knitmd=knitmd, parentWikiId=NULL)
}

createAndKnitToFolderEntity(file = "individual-cohorts/meta_analysis/meta-analysis_diagnosis.Rmd",
                                          parentId ="syn22315403",
                                          folderName = 'Meta-analysis on diagnosis',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

### 2020-09-01 individual-cohorts/meta_analysis/meta-analysis_sex.Rmd
Freeze analysis

```{r knit2synapse, eval=FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "individual-cohorts/meta_analysis/meta-analysis_sex.Rmd",
                                          parentId ="syn22315403",
                                          folderName = 'Meta-analysis on sex',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

>>>>

```{r knit2synapse, eval=FALSE, echo=FALSE}

createAndKnitToFolderEntity <- function(file, parentId, folderName,
                                        wikiName=NULL, overwrite=FALSE, knitmd=TRUE, ...) {

  entity <- synapser::Folder(parentId=parentId, name=folderName)
  entity <- synapser::synStore(entity, ...)

  knitfile2synapse(file=file, owner=entity, wikiName=wikiName, 
                   overwrite=overwrite, knitmd=knitmd, parentWikiId=NULL)
}

library(synapser)
library(knit2synapse)
synLogin()
# knit2synapse::
createAndKnitToFolderEntity(file = "individual-cohorts/meta_analysis/meta-analysis_sex.Rmd",
                                          parentId ="syn22315403",
                                          folderName = 'Meta-analysis on sex',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```
